### 2018-03-20 mftpc/slide-intro.tex
mftpc: Import corresponding to 2018-2

Your oscillators quiver in simulated excitement in anticipation of
the robot dance party in honor of $2^6$th birthdays---%
in particular, that of Harry Qbit Bovik---%
which you now approach.
With the doors to the SIGBOVIK 2018 dance party looming ahead,
you prefetch the 31 specimens of top-notch research,
readying yourself to discuss, enjoy, and perhaps even do follow-up work on
the brilliant research contained therein.
After scanning them in reverse-alphabetical order by first author name,
you are fully prepared.
You push open the daunting dance party doors...
and realize there's been a \texttt{MAX\_UINT64\_T}-sized mistake.

@@

Audio thumps in the artificially limited 20--20000~Hz range
as humans dance, converse,
and sip on dangerously conductive beverages.
You make your way through the crowd, attempting to appear human.
It's a dangerous world for robots:
any of these humans might be a Serious Researcher
who wants to reprogram you with Serious Research Code!

>>>>

Your oscillators quiver in simulated excitement in anticipation of
the robot dance party in honor of $2^6$th birthdays---%
in particular, that of Harry Qubit Bovik---%
which you now approach.
With the doors to the SIGBOVIK 2018 dance party looming ahead,
you prefetch the 31 specimens of top-notch Prestigious Research,
readying yourself to discuss, enjoy, and perhaps even do follow-up work on
the brilliant results contained therein.
After scanning them in reverse-alphabetical order by first author name,
you are fully prepared.
You push open the daunting dance party doors...
and quickly realize that you've made a \texttt{MAX\_UINT64\_T}-sized mistake.

@@

Audio thumps in the artificially limited 20--20000~Hz range
as humans dance, converse,
and sip on dangerously conductive beverages.
You weave your way through the crowd, attempting to appear human.
It's a dangerous world for robots:
any of these humans might be a Serious Researcher
who wants to reprogram you with Serious Research Code!
